Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2023-03-15 latex/comp_or.tex
mpShims still worst
Paper COR updated

{\color{blue} Each node, except the base, inherits information from the previous nodes (pallets that must remain on board), and must solved taking into account the remaining not visited nodes. One more reason for a node-by-node approach.}

@@

\subsubsection{{\it Shims} third and fourth phases}

@@

Algorithm \ref{alg:getBestShims} describes the procedure do get the best {\it Shims}, the best subset of edges to fill each pallet gap. This algorithm follows the logic of the {\it First-Fit Decreasing} algorithm as described by \cite{JohnsonGarey1985}.

Line \ref{empty_shims} creates the first empty shims.
Line \ref{empty_set} creates the first set of shims from where the best shims will be chosen.

@@

		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}                       & $f$                &     10.34 &     8.50  &     12.42 &     15.06 &     15.97 &     15.88 &  0.96 \\% 7817
		&                                                & {\it run time (s)} &     < 1   &     3     &     5     &     20    &     58    &     352   &  1.0 \\% 439

		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}                     & $f$                &     11.73 &     7.57  &     12.05 &     12.95 &     13.94 &     13.62 & 0.88 \\% 7186

		&                                                & {\it run time (s)} &     < 1   &     2     &     3     &     16    &     33    &     193   &  {\bf 1.8}\\% 248

@@

		\multirow{6}{*}{$1.5$}&\specialcell{$Relaxed$\\$Gurobi$}& $f$         &{\it }&{\it  } &{\it  }&{\it  }&{\it  }&{\it  }&  \specialcell{{\bf 1.00}\\-} \\%

        \cmidrule{2-10}		                       
        &\multirow{2}{*}{ $Shims$}                       & $f$                &     14.68 &   12.21   &  17.67    &  21.01    &  22.64    &       &    \\% 
        &                                                & {\it run time (s)} &     < 1   &     2     &     3     &     12    &     33    &        &  1.0 \\%

        \cmidrule{2-10}		                       
        &\multirow{2}{*}{ $mpShims$}                     & $f$                &       &        &       &       &       &       &   \\% 7186
        &                                                & {\it run time (s)} &     < 1   &     2     &     3     &     16    &     33    &     193   &  {\bf 1.8}\\% 248

@@

We solved all scenarios and instances with Gurobi in a relaxed linear model, {\it Relaxed Gurobi}. This is good for the reader to have an idea of the real performance differences between serial and parallel {\it Shims}.

{\it Shims} had a quality performance very close to the {\it Relaxed Gurobi} upper bound solution, and, as to the {\bf Speedup}, on average, {\it mpShims} was 1.8 times faster than {\it Shims}. Theoretically, it could be more, but due to the burden of sharing the CG deviation and the list of items among the processes (pallets) for reading and writing, the execution {\it race condition} management limited {\it mpShims} performance.

@@

We confirmed the hypothesis raised in line \ref{mpShims:minCGdev} of Algorithm \ref{alg:mpShims} that, in sequential mode, where one pallet is built at a time, torque constraints could be more restrictive than volume or weight constraints, which could stop the palletization process earlier, fostering a solution that may be not as good as it could be. This integer programming procedure inclusion really improved {\it Shims} results.

@@

There was some expectation on this post-improvement method as it could have minimized the distances of travel of the pallets to the ramp door, but unfortunately, there was no alteration to these distances.

>>>>

Each node, except the base, inherits information from the previous nodes (pallets that must remain on board), and must be solved taking into account the remaining not visited nodes. One more reason for a node-by-node approach.

@@

\subsubsection{{\it Shims} third phase}

@@

Algorithm \ref{alg:getBestShims} describes the procedure to get the top {\it Shims}, the best subset of edges to fill each pallet gap. This algorithm follows the logic of the {\it First-Fit Decreasing} method as described by \cite{JohnsonGarey1985}. Although it does not aim to minimize the number of bins, its mechanism helped build the set of {\it Shims} to allow the best to be chosen.

Line \ref{empty_shims} creates the first empty shims.
Line \ref{empty_set} produce the first set of shims from where the best shims will be chosen.

@@

		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}                       & $f$                &     10.34 &     8.50  &     12.42 &     15.06 &     15.97 &     15.88 &  0.96 \\% 7817
		&                                                & {\it run time (s)} &     < 1   &     3     &     5     &     20    &     58    &     352   &  1.0 \\% 439			
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}                     & $f$                &   12.96   &   7.53    &  12.28    &   13.20   &  13.71    &   13.44   &  0.90\\% 7278
		&                                                & {\it run time (s)} &     < 1   &     2     &     2     &     8    &     22    &     120   &  {\bf 2.8}\\%

@@

		\multirow{6}{*}{$1.5$}&\specialcell{$Relaxed$\\$Gurobi$}& $f$         &{\it 17.01}&{\it 12.45}&{\it 18.02}&{\it 22.03}&{\it 23.09}&{\it 22.35}&  \specialcell{{\bf 1.00}\\-} \\%11495

        \cmidrule{2-10}		                       
        &\multirow{2}{*}{ $Shims$}                       & $f$                &     14.68 &     12.21 &     17.67 &  21.01    &  22.64    &   21.91   &  0.96  \\%  11012
        &                                                & {\it run time (s)} &     < 1   &     2     &     3     &     12    &     33    &   209     &  1.0 \\% 260

        \cmidrule{2-10}		                       
        &\multirow{2}{*}{ $mpShims$}                     & $f$                &    16.12  &     11.81 &     17.48 &  17.66    &   19.81   &  17.61    &  0.87 \\% 9966
        &                                                & {\it run time (s)} &     < 1   &     1     &     2     &     7     &   20      &  120      &  {\bf 1.7}\\% 151

		\midrule
		\multirow{6}{*}{$2.0$}&\specialcell{$Relaxed$\\$Gurobi$}& $f$         &{\it 24.56}&{\it 17.47}&{\it 25.19}&{\it 27.94}&{\it  }&{\it  }&  \specialcell{{\bf 1.00}\\-} \\%11495

		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}                       & $f$                &    21.31  &  17.35    &   24.24   &   27.39    &  29.31     &  27.06     &     \\%  11012
		&                                                & {\it run time (s)} &     < 1   &     2     &     4     &     14     &     35     &   220     &  1.0 \\% 260

		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}                     & $f$                &    24.33  &   17.26   &   24.70   &  24.81     &   27.71    &  24.93        &    \\% 9966
		&                                                & {\it run time (s)} &     < 1   &     2     &     3     &     9      &   26       &  151      &  {\bf 1.7}\\% 151

@@

We solved all scenarios and instances with {\it Gurobi} in a relaxed linear model, {\it Relaxed Gurobi}. This is good for the reader to have an idea of the real performance differences between serial and parallel {\it Shims}.

{\it Shims} had a quality performance very close to the {\it Relaxed Gurobi} upper bound solution, and, as to the {\bf Speedup}, on average, {\it mpShims} was .... times faster than {\it Shims}. Theoretically, it could be more, but due to the burden of sharing the CG deviation and the list of items among the processes (pallets) for reading and writing, the execution {\it race condition} management limited {\it mpShims} performance.

@@

We confirmed the hypothesis raised in line \ref{mpShims:minCGdev} of Algorithm \ref{alg:mpShims} that, in sequential mode, where one pallet is built at a time, torque constraints could be more restrictive than volume or weight constraints, which could stop the palletization process earlier, fostering a solution that may be not as good as it could be. This integer programming procedure inclusion really improved all {\it Shims} results.

@@

There was some expectation on this post-improvement method as it could have minimized the distances of travel of the pallets to the ramp door, but unfortunately, after running all scenarios and problem instances, there was no improvement in minimizing these distances.

This proves that the solutions provided by {\it Shims} and {\it mpShims} are tight enough to hinder this intended improvement.
